Self Regulation Ontology Retest Data Report

### 2017-11-21 code/SRO_Report.Rmd
adding new analyses

@@

>>>>

One way to solve this would be to feed data in manually.

@@

```{r}
t1_2_difference %>%
  left_join(measure_labels[,c("dv", "overall_difference", "raw_fit", "rt_acc")], by= "dv") %>%
  filter(overall_difference == "overall",
         rt_acc %in% c("rt", "accuracy"),
         task == "task") %>%
  group_by(dv) %>%
  summarise(mean_diff = mean(difference),
            task_name = unique(task_name),
            rt_acc = unique(rt_acc)) %>%  
  ggplot(aes(dv,mean_diff, color=task_name))+
  geom_point()+
  theme_bw()+
  facet_grid(~rt_acc)+
  theme(legend.position = "none",
        axis.text.x = element_blank())+
  xlab("Dependent variable")+
  ylab("Average difference between time points")
```

```{r}
tmp = t1_2_difference %>%
  left_join(measure_labels[,c("dv", "overall_difference", "raw_fit", "rt_acc")], by= "dv") %>%
  filter(overall_difference == "overall",
         rt_acc %in% c("accuracy"),
         task == "task") %>%
  group_by(dv) %>%
  summarise(mean_diff = mean(difference),
            task_name = unique(task_name))

t.test(tmp$mean_diff)
```

Write new function to estimate reliability accounting for learning effect

```{r}
get
```
